%  This file is part of pdfpc.
%  Copyright (C) 2020 Evgeny Stambulchik
%
%  This program is free software; you can redistribute it and/or modify
%  it under the terms of the GNU General Public License as published by
%  the Free Software Foundation; either version 3 of the License, or
%  (at your option) any later version.
%
%  This program is distributed in the hope that it will be useful,
%  but WITHOUT ANY WARRANTY; without even the implied warranty of
%  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
%  GNU General Public License for more details.
%
%  You should have received a copy of the GNU General Public License along
%  with this program; if not, write to the Free Software Foundation, Inc.,
%  51 Franklin Street, Fifth Floor, Boston, MA 02110-1301 USA.
%  -------------------------------------------------------------------------------------------
%
%  Allow for defining some meta data and simple textual notes for use
%  with the pdfpc presentation application <https://pdfpc.github.io>.
%
%  -------------------------------------------------------------------------------------------
%
%  Inspired by Carsten Brandt's <https://github.com/cebe/pdfpc-latex-notes>.
%
%  -------------------------------------------------------------------------------------------
%
%  Please report bugs and other problems as well as suggestions for improvements
%  to the issue tracker at github <https://github.com/pdfpc/pdfpc/>
%
%  -------------------------------------------------------------------------------------------
\documentclass[11pt]{ltxdoc}

\usepackage{iftex}

\usepackage[english]{babel}

\usepackage{hyperref}

\newcommand*{\sty}[1]{\textsf{#1}}
\def\param#1{\textit{\rmfamily\mdseries\ensuremath{\langle}#1\ensuremath{\rangle}}}


\title{The \sty{pdfpc} package \\ {\large\url{https://github.com/pdfpc/pdfpc}}}
\author{Evgeny Stambulchik}
\date{2020/12/05 (v0.5.1)}

\hypersetup{pdftitle={The pdfpc package}, pdfauthor={Evgeny Stambulchik}}

\begin{document}
\maketitle
\thispagestyle{empty}

\begin{abstract}
This package provides  a convenient way to specify notes and to define certain
meta  properties  of the  presentation when used with
\href{https://pdfpc.github.io/}{PDF Presenter Console (\texttt{pdfpc}), a
GPLv2+ licensed multi-monitor PDF presentation viewer application available on
GitHub}\footnote{\url{https://pdfpc.github.io/}}.
\end{abstract}

\clearpage
\section*{Dependencies and other requirements}

\sty{pdfpc} requires the use of \LaTeXe.

It depends on the following packages:

\begin{multicols}{3}\sffamily\centering
kvoptions \\ xstring \\ hyperxmp
\end{multicols}

\section*{License}

\textcopyright\ 2020 Evgeny Stambulchik

This program is free software; you can redistribute it and/or modify
it under the terms of the GNU General Public License as published by
the Free Software Foundation; either version 3 of the License, or
(at your option) any later version.

This work consists of the following files:

\begin{itemize}
    \item "pdfpc.sty",
    \item "pdfpc-doc.tex"
    \item "pdfpc-doc.pdf" \emph{(compiled)}
\end{itemize}

\clearpage

\part{The documentation}
\section*{Loading \sty{pdfpc}}

Load \sty{pdfpc} by adding \cmd{\usepackage\{pdfpc\}} to your preamble.

The following \param{options} may be given as comma-separated list:

\begin{itemize}
\item \texttt{duration}
\item \texttt{starttime}
\item \texttt{endtime}
\item \texttt{enduserslide}
\item \texttt{lastminutes}
\item \texttt{hidenotes}
\item \texttt{overridenote}
\item \texttt{disablemarkdown}
\item \texttt{defaulttransition} (needs pdfpc v4.5 or higher)
\end{itemize}

The meaning and possible values of most of these options are documented in
\textit{pdfpcrc(5)} man page of the pdfpc program. The rest are explained below.

To add a note to a slide, use \cmd{\pdfpcnote\{Text of a note\}}. A line break
in the body of the note can be inserted with \cmd{\\}. The notes are rendered
according to the Markdown syntax by default. If you prefer the plain text format
(which was the case with \texttt{pdfpc}-4.4 and below), use the
\texttt{disablemarkdown} option.

The pdfpc package can be used standalone or together with beamer. In
the later case, it may be desirable to continue using the \cmd{\note}
command. To this end, the \texttt{overridenote} option should be provided.
Please note though, that this will work only in simple cases.

If you prefer using full-featured beamer notes rendered alongside the
presentation (\cmd{\setbeameroption\{show notes on second screen\}}), the pdfpc
package will autodetect it, so using the \texttt{--notes} command-line option is
unnecessary. To override the autodetection, use the \texttt{notesposition}
option, accepting the same values (right/left/top/bottom/none).

When sharing slides, one may want to omit the (private) notes, by using the
\texttt{hidenotes} option. Enabling it together with \texttt{overridenote} will
disable the beamer notes as well.

\StopEventually{%
    \clearpage
    \PrintChanges}
\clearpage

\Finale
\end{document}
